Political Support in the United States

### 2024-03-16 paper/paper.qmd
Update paper.qmd

# Introduction
Introduction:

@@

The Cooperative Election Study (CES) addressed gaps in understanding voter behavior by employing a multifaceted approach involving 60,000 cases and 60 research teams. Their methods included pre-election surveys and post-election assessments, providing detailed insights into American elections. Pre-election surveys were filled out on the spot between September 29 and November 8. The Post-election campaigning frenzy took place between November 10 and December 15. For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team. Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content. Every one of the sixty teams bought a 1,000-person survey. Every case was chosen online, and YouGov created a corresponding random sample for this investigation. The first data release happened on March 20, 2023. The Harvard University database contains archived and accessible data from this investigation. Vote verification is included in data release 2 for all respondents. The study on CES 2022 is still under progress. Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation. The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.

Understanding these findings is crucial for policymakers, researchers, and citizens, as they shed light on the complexities of democracy and provide insights to strengthen democratic institutions. This paper aims to dive deeper into the CES findings, analyzing their implications for the future of American democracy.

>>>>

# Introduction

@@

The Cooperative Election Study (CES) addressed gaps in understanding voter behavior by employing a multifaceted approach involving 60,000 cases and 60 research teams. Their methods included pre-election surveys and post-election assessments, providing detailed insights into American elections. Pre-election surveys were filled out on the spot between September 29 and November 8. The Post-election campaigning frenzy took place between November 10 and December 15. For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team. Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content. Every one of the sixty teams bought a 1,000-person survey. Every case was chosen online, and YouGov created a corresponding random sample for this investigation. The first data release happened on March 20, 2023. The Harvard University database contains archived and accessible data from this investigation. Vote verification is included in data release 2 for all respondents. The study on CES 2022 is still under progress. Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation. The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005. Understanding these findings is crucial for policymakers, researchers, and citizens, as they shed light on the complexities of democracy and provide insights to strengthen democratic institutions. This paper aims to dive deeper into the CES findings, analyzing their implications for the future of American democracy.

The data utilized for analysis, including both survey and census data, is in Section 2. Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes. I will also talk about the predicted results derived from the model in Section 4. Lastly, Section 5 contains the results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language R (R Core Team 2022). The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al. 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al. 2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
2024).
